Simulation Study: Varying Null Proportion

### 2018-08-06 datasets/simulations/simulations-varyingpi0.Rmd

```{r null05-run-simulation}
if (file.exists(null05_file)) {
    res <- readRDS(null05_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null05_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null05-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null05-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

@@

```{r null10-run-simulation}
if (file.exists(null10_file)) {
    res <- readRDS(null10_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null10_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null10-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null10-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

@@

```{r null20-run-simulation}
if (file.exists(null20_file)) {
    res <- readRDS(null20_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null20_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null20-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null20-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

@@

```{r null30-run-simulation}
if (file.exists(null30_file)) {
    res <- readRDS(null30_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null30_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null30-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null30-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

@@

```{r null40-run-simulation}
if (file.exists(null40_file)) {
    res <- readRDS(null40_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null40_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null40-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null40-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

@@

```{r null50-run-simulation}
if (file.exists(null50_file)) {
    res <- readRDS(null50_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null50_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null50-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null50-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

@@

```{r null60-run-simulation}
if (file.exists(null60_file)) {
    res <- readRDS(null60_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null60_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null60-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null60-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

@@

```{r null70-run-simulation}
if (file.exists(null70_file)) {
    res <- readRDS(null70_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null70_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null70-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null70-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

@@

```{r null80-run-simulation}
if (file.exists(null80_file)) {
    res <- readRDS(null80_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null80_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null80-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null80-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

@@

```{r null90-run-simulation}
if (file.exists(null90_file)) {
    res <- readRDS(null90_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null90_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null90-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null90-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

@@

```{r null95-run-simulation}
if (file.exists(null95_file)) {
    res <- readRDS(null95_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null95_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null95-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null95-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

@@

```{r null99-run-simulation}
if (file.exists(null99_file)) {
    res <- readRDS(null99_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null99_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null99-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null99-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

>>>>

```{r null05-run-simulation}
if (file.exists(null05_file)) {
    res <- readRDS(null05_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, es_dist = es_dist, icovariate = icovariate,
                    ts_dist = ts_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null05_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null05-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, es_dist = es_dist, ts_dist = ts_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null05-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 10, numQ = 3)
```

@@

```{r null10-run-simulation}
if (file.exists(null10_file)) {
    res <- readRDS(null10_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, es_dist = es_dist, icovariate = icovariate,
                    ts_dist = ts_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null10_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null10-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, es_dist = es_dist, ts_dist = ts_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null10-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 10, numQ = 3)
```

@@

```{r null20-run-simulation}
if (file.exists(null20_file)) {
    res <- readRDS(null20_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, es_dist = es_dist, icovariate = icovariate,
                    ts_dist = ts_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null20_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null20-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, es_dist = es_dist, ts_dist = ts_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null20-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 10, numQ = 3)
```

@@

```{r null30-run-simulation}
if (file.exists(null30_file)) {
    res <- readRDS(null30_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, es_dist = es_dist, icovariate = icovariate,
                    ts_dist = ts_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null30_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null30-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, es_dist = es_dist, ts_dist = ts_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null30-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 10, numQ = 3)
```

@@

```{r null40-run-simulation}
if (file.exists(null40_file)) {
    res <- readRDS(null40_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, es_dist = es_dist, icovariate = icovariate,
                    ts_dist = ts_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null40_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null40-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, es_dist = es_dist, ts_dist = ts_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null40-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 10, numQ = 3)
```

@@

```{r null50-run-simulation}
if (file.exists(null50_file)) {
    res <- readRDS(null50_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, es_dist = es_dist, icovariate = icovariate,
                    ts_dist = ts_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null50_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null50-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, es_dist = es_dist, ts_dist = ts_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null50-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 10, numQ = 3)
```

@@

```{r null60-run-simulation}
if (file.exists(null60_file)) {
    res <- readRDS(null60_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, es_dist = es_dist, icovariate = icovariate,
                    ts_dist = ts_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null60_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null60-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, es_dist = es_dist, ts_dist = ts_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null60-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 10, numQ = 3)
```

@@

```{r null70-run-simulation}
if (file.exists(null70_file)) {
    res <- readRDS(null70_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, es_dist = es_dist, icovariate = icovariate,
                    ts_dist = ts_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null70_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null70-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, es_dist = es_dist, ts_dist = ts_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null70-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 10, numQ = 3)
```

@@

```{r null80-run-simulation}
if (file.exists(null80_file)) {
    res <- readRDS(null80_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, es_dist = es_dist, icovariate = icovariate,
                    ts_dist = ts_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null80_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null80-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, es_dist = es_dist, ts_dist = ts_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null80-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 10, numQ = 3)
```

@@

```{r null90-run-simulation}
if (file.exists(null90_file)) {
    res <- readRDS(null90_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, es_dist = es_dist, icovariate = icovariate,
                    ts_dist = ts_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null90_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null90-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, es_dist = es_dist, ts_dist = ts_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null90-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 10, numQ = 3)
```

@@

```{r null95-run-simulation}
if (file.exists(null95_file)) {
    res <- readRDS(null95_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, es_dist = es_dist, icovariate = icovariate,
                    ts_dist = ts_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null95_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null95-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, es_dist = es_dist, ts_dist = ts_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null95-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 10, numQ = 3)
```

@@

```{r null99-run-simulation}
if (file.exists(null99_file)) {
    res <- readRDS(null99_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, es_dist = es_dist, icovariate = icovariate,
                    ts_dist = ts_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null99_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```

@@

```{r null99-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, es_dist = es_dist, ts_dist = ts_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

@@

```{r, null99-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 10, numQ = 3)
```
